---
title: "`netcopula` package"
subtitle: "Report at 2016-04-12"
author: "Sergio Venturini"
date: ''
# output: rmarkdown::html_vignette
output:
  pdf_document:
    highlight: zenburn
#    toc: yes
  html_document:
    highlight: tango
    self-contained: yes
    standalone: yes
    theme: united
#    toc: yes
header-includes: \usepackage{bm}
vignette: >
  %\VignetteIndexEntry{Report at 2016-04-12}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Trace plots for a subset of the parameters

```{r prior, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
library(netcopula)

load(file = "~/dev/netcopula/demo/tmp/examples_1.RData")
if (!.hasSlot(res, "S_q")) {
  res@S_q <- array()
  res@Sigma_q_prop <- array()
  res@rho_mu <- array()
  res@cov_mu <- array()
  res@ar_mu_vec <- array()
  res@mu_rate <- array()
  res@mu_prop <- array()
  res@tp_mu <- array()
  res@delta_prop <- array()
  res@data <- nc_data
}

## MCMC diagnostics
par(mfrow = c(3, 2), mar = c(2.5, 3, 2, 2))
plot(res@Gamma[1, 1, ], type = "l", main = "Gamma (treatment = 1, element [2, 1])", cex.main = 1.5)
plot(as.numeric(res@Sigma[, 6]), type = "l", main = "Sigma_M (element [3,3])", cex.main = 1.5)
plot(res@mu[2, 1, ], type = "l", main = "mu (study 2 - outcome = 1)", cex.main = 1.5)
plot(res@delta[2, 1, ], type = "l", main = "delta (study 2 - outcome = 1)", cex.main = 1.5)
plot(res@d[2, 1, ], type = "l", main = "d (treatment 2 - outcome = 1)", cex.main = 1.5)
plot(res@x[10, 2, ], type = "l", main = "x (arm 10 - outcome = 1)", cex.main = 1.5)
```

\newpage

# $(\mu_{ikm}, \delta_{ikm})$ target density

The following plots are obtained using:
\begin{itemize}
\item $\tau_{ikm} = 0$
\item $\eta_{ikm} = 1$
\item $y_{ikm} = 20$
\item $n_{ikm} = 80$
\item $\omega_{ikm} = 0$
\item $\gamma_{ikm} = 1$
\item $\mu_{\sigma} = \sqrt{10^3}$
\item $\varepsilon = 1E-12$
\end{itemize}

```{r mu_delta_1, echo=FALSE, fig.height=8.5, fig.width=8.5, message=FALSE, warning=FALSE}
mu_delta_r <- function(mu, delta, tau, eta, y, n, w, gamma, mu_sigma, eps, eps_ab) {
  theta <- mu + delta
  p <- expit_rcpp(theta)

  a <- pbinom(y - 1, n, p, 1, 0)
  b <- pbinom(y, n, p, 1, 0)
  if (a > (1 - eps_ab)) {
    a <- 1 - eps_ab
  } else if (a < eps_ab) {
    a <- eps_ab
  }
  if (b > (1 - eps_ab)) {
    b <- 1 - eps_ab
  } else if (b < eps_ab) {
    b <- eps_ab
  }
  eps_a <- a/2.0
  eps_b <- (1.0 - b)/2.0
  if (a == b) {
    if (a == 0) {
      b <- b + eps
    } else if (b == 1) {
      a <- a - eps
    } else {
      a <- a - min(eps/2.0, eps_a)
      b <- b + min(eps/2.0, eps_b)
    }
  }
  phi_inv_a <- qnorm(a, 0.0, 1.0, 1, 0)
  phi_inv_b <- qnorm(b, 0.0, 1.0, 1, 0)
  tmp <- pnorm((phi_inv_b - w)/gamma, 0.0, 1.0, 1, 0) - pnorm((phi_inv_a - w)/gamma, 0.0, 1.0, 1, 0)

  if (!is.finite(tmp)) {
    return(NA)
  }

  return(tmp)
}

mu_delta_func <- function(theta, varargs) {
  mu <- theta[1]
  delta <- theta[2]
  tau <- varargs$tau
  eta <- varargs$eta
  y <- varargs$y
  n <- varargs$n
  w <- varargs$w
  gamma <- varargs$gamma
  mu_sigma <- varargs$mu_sigma
  eps <- varargs$eps
  eps_ab <- varargs$eps_ab

  return(mu_delta_r(mu, delta, tau, eta, y, n, w, gamma, mu_sigma, eps, eps_ab))
}

par <- c(0, 0)
tau <- 0
eta <- 1
y <- 20
n <- 80
w <- 0
gamma <- 1
mu_sigma <- sqrt(prm_prior$mu_sigma2)
eps <- 1e-12
eps_ab <- 1e-8

args <- list(tau = tau, eta = eta, y = y, n = n, w = w, gamma = gamma, mu_sigma = mu_sigma, eps = eps, eps_ab = eps_ab)
options <- list(trace = 0, fnscale = -1, parscale = c(1, 1), ndeps = c(0.001, 0.001), maxit = 500, abstol = -Inf, reltol = sqrt(.Machine$double.eps), alpha = 1, beta = 0.5, gamma = 2)

res <- optim_rcpp(par, mu_delta_func, args, options, hessian = TRUE)

limits <- c(-2, 1, -1, .5)
par(mfrow = c(2, 2))
my_plot(mu_delta_func, limits, args, type = "persp", npoints = 70, xlab = "mu", ylab = "delta", theta = 10, phi = 20, main = "3D plot", cex.main = 1.5)
my_plot(mu_delta_func, limits, args, type = "contour", npoints = 100, xlab = "mu", ylab = "delta", nlevels = 10, main = "Contour plot", cex.main = 1.5)
abline(v = res$par[1], lty = 2)
abline(h = res$par[2], lty = 2)
points(res$par[1], res$par[2], pch = 19)
# text(res$par[1] - .6, res$par[2] + .1, labels = "Maximum", cex = .8, pos = 2)

delta <- 0
mu <- seq(-5, 5, by = .01)
mu_val <- numeric(length(mu))
for (i in 1:length(mu)) {
  par <- c(mu[i], delta)
  mu_val[i] <- mu_delta_func(par, args)
}
plot(mu, mu_val, type = "l", ylab = "")

mu <- -2
delta <- seq(-5, 5, by = .01)
delta_val <- numeric(length(delta))
for (i in 1:length(delta)) {
  par <- c(mu, delta[i])
  delta_val[i] <- mu_delta_func(par, args)
}
plot(delta, delta_val, type = "l", ylab = "")
```

\newpage

The following plots are obtained using:
\begin{itemize}
\item $\tau_{ikm} = 0$
\item $\eta_{ikm} = 1$
\item $y = 80$ (in the previous plots this was $20$)
\item $n_{ikm} = 80$
\item $\omega_{ikm} = 0$
\item $\gamma_{ikm} = 1$
\item $\mu_{\sigma} = \sqrt{10^3}$
\item $\varepsilon = 1E-12$
\end{itemize}

```{r, echo=FALSE, fig.height=8.5, fig.width=8.5, message=FALSE, warning=FALSE}
par <- c(10, 10)
tau <- 0
eta <- 1
y <- 80
n <- 80
w <- 0
gamma <- 1
mu_sigma <- sqrt(prm_prior$mu_sigma2)
eps <- 1e-12
eps_ab <- 1e-8

args <- list(tau = tau, eta = eta, y = y, n = n, w = w, gamma = gamma, mu_sigma = mu_sigma, eps = eps, eps_ab = eps_ab)
options <- list(trace = 0, fnscale = -1, parscale = c(1, 1), ndeps = c(0.001, 0.001), maxit = 500, abstol = -Inf, reltol = sqrt(.Machine$double.eps), alpha = 1, beta = 0.5, gamma = 2)

res <- optim_rcpp(par, mu_delta_func, args, options, hessian = TRUE)

limits <- c(-2, 15, -1, 15)
par(mfrow = c(2, 2))
my_plot(mu_delta_func, limits, args, type = "persp", npoints = 70, xlab = "mu", ylab = "delta", theta = 10, phi = 20, main = "3D plot", cex.main = 1.5)
my_plot(mu_delta_func, limits, args, type = "contour", npoints = 100, xlab = "mu", ylab = "delta", nlevels = 10, main = "Contour plot", cex.main = 1.5)
abline(v = res$par[1], lty = 2)
abline(h = res$par[2], lty = 2)
points(res$par[1], res$par[2], pch = 19)
# text(res$par[1], res$par[2], labels = "Maximum", cex = .8, pos = 2)

delta <- 0
mu <- seq(-5, 15, by = .01)
mu_val <- numeric(length(mu))
for (i in 1:length(mu)) {
  par <- c(mu[i], delta)
  mu_val[i] <- mu_delta_func(par, args)
}
plot(mu, mu_val, type = "l", ylab = "")

mu <- -2
delta <- seq(-5, 15, by = .01)
delta_val <- numeric(length(delta))
for (i in 1:length(delta)) {
  par <- c(mu, delta[i])
  delta_val[i] <- mu_delta_func(par, args)
}
plot(delta, delta_val, type = "l", ylab = "")
```
