---
title: '`netcopula` package'
author: "Sergio Venturini"
date: ''
# output: rmarkdown::html_vignette
output:
  pdf_document:
    highlight: zenburn
#    keep_tex: yes
  html_document:
    highlight: tango
    self-contained: yes
    standalone: yes
    theme: united
#  word_document: default
subtitle: Report at `r Sys.Date()`
header-includes: \usepackage{bm}
vignette: >
  %\VignetteIndexEntry{Report at `r Sys.Date()`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r global_options, include=FALSE}
# knitr::opts_chunk$set(warning=FALSE, message=FALSE, comment='')
path <- "~/dev/netcopula/demo/tmp"
library(netcopula)
```

# Using \emph{all the data} from Achana et al. (2014) (i.e. imputing the missing outcomes)

All the latent variables are estimated, tha is, we do not use the imputation algorithm.

```{r loading_1, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
load(file = file.path(path, "examples_10.RData"))
```

## $\boldsymbol{\Gamma}$ (outcome copula correlation matrix)

Here, the $\boldsymbol{\Gamma}$ matrix is not estimated, but it is constrained to be equal to the identity matrix.

## $\boldsymbol{\Sigma}_M$ (common between-study covariance structure)

```{r Sigma_M_1, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, results="asis"}
plot(x = res, to_plot = "Sigma_M", type = "trace")
cat("\\clearpage")
plot(x = res, to_plot = "Sigma_M", type = "caterpillar")
```

```{r Corr_M_1, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, results="asis"}
plot(x = res, to_plot = "Corr_M", type = "trace")
cat("\\clearpage")
plot(x = res, to_plot = "Corr_M", type = "caterpillar")
```

## $\boldsymbol{\mu}$ (study-specific baseline effects)

```{r mu_1, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, results="asis"}
plot(x = res, to_plot = "mu", type = "trace")
cat("\\clearpage")
plot(x = res, to_plot = "mu", type = "caterpillar")
```

## $\boldsymbol{\delta}$ (study-specific [random] treatment effects)

```{r delta_1, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, results="asis"}
plot(x = res, to_plot = "delta", type = "trace")
cat("\\clearpage")
plot(x = res, to_plot = "delta", type = "caterpillar")
```

## $\boldsymbol{d}$ (pooled treatment effects across trials)

```{r d_1, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, results="asis"}
plot(x = res, to_plot = "d", type = "trace")
cat("\\clearpage")
plot(x = res, to_plot = "d", type = "caterpillar")
```

## $\boldsymbol{x}$ (latent variables)

```{r x_1, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, results="asis"}
plot(x = res, to_plot = "x", latent_var = TRUE, type = "trace")
cat("\\clearpage")
plot(x = res, to_plot = "x", latent_var = TRUE, type = "caterpillar")
```

# Using \emph{only complete data} for the first two outcomes from Achana et al. (2014)

All the latent variables are estimated, tha is, we do not use the imputation algorithm.

```{r loading_2, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
load(file = file.path(path, "examples2_10.RData"))
```

## $\boldsymbol{\Gamma}$ (outcome copula correlation matrix)

Here, the $\boldsymbol{\Gamma}$ matrix is not estimated, but it is constrained to be equal to the identity matrix.

## $\boldsymbol{\Sigma}_M$ (common between-study covariance structure)

```{r Sigma_M_2, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, results="asis"}
plot(x = res, to_plot = "Sigma_M", type = "trace")
cat("\\clearpage")
plot(x = res, to_plot = "Sigma_M", type = "caterpillar")
```

```{r Corr_M_2, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, results="asis"}
plot(x = res, to_plot = "Corr_M", type = "trace")
cat("\\clearpage")
plot(x = res, to_plot = "Corr_M", type = "caterpillar")
```

## $\boldsymbol{\mu}$ (study-specific baseline effects)

```{r mu_2, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, results="asis"}
plot(x = res, to_plot = "mu", type = "trace")
cat("\\clearpage")
plot(x = res, to_plot = "mu", type = "caterpillar")
```

## $\boldsymbol{\delta}$ (study-specific [random] treatment effects)

```{r delta_2, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, results="asis"}
plot(x = res, to_plot = "delta", type = "trace")
cat("\\clearpage")
plot(x = res, to_plot = "delta", type = "caterpillar")
```

## $\boldsymbol{d}$ (pooled treatment effects across trials)

```{r d_2, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, results="asis"}
plot(x = res, to_plot = "d", type = "trace")
cat("\\clearpage")
plot(x = res, to_plot = "d", type = "caterpillar")
```

## $\boldsymbol{x}$ (latent variables)

```{r x_2, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, results="asis"}
plot(x = res, to_plot = "x", latent_var = TRUE, type = "trace")
cat("\\clearpage")
plot(x = res, to_plot = "x", latent_var = TRUE, type = "caterpillar")
```
