---
title: '`netcopula` package'
author: "Sergio Venturini"
date: ''
# output: rmarkdown::html_vignette
output:
  pdf_document:
    highlight: zenburn
#    keep_tex: yes
  html_document:
    highlight: tango
    self-contained: yes
    standalone: yes
    theme: united
  word_document: default
subtitle: Report at 2016-04-20`
header-includes: \usepackage{bm}
vignette: >
  %\VignetteIndexEntry{Report at 2016-04-20}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r global_options, include=FALSE}
# knitr::opts_chunk$set(warning=FALSE, message=FALSE, comment='')
path <- "~/dev/netcopula/demo/tmp"
gen_res <- function(to_plot) {
  to_keep <- substr(rownames(out), 1, nchar(to_plot) + 1) == paste0(to_plot, "[")
  tmp <- out[to_keep, ]
  caterplot(res_mcmc, to_plot, reorder = TRUE, quantiles = list(outer = c(0.025, 0.975), inner = c(0.1, 0.9)))
  caterpoints(tmp[sort.int(tmp[, 5], decreasing = TRUE, index.return = TRUE)$ix, 1], pch = "x", col = "darkorange")
  title(paste0("parameters ", to_plot, " (data from Achana et al., 2014)"), cex.main = 1.25)
  
  traplot(res_mcmc, parms = to_plot, mar = c(1.0, 1.5, .75, .15) + .1, col = NULL, lty = 1, plot.title = NULL, main = NULL, greek = FALSE, style = "plain", cex.main = .85, cex.axis = .7, tcl = -.3, xaxt = "n")
}
```

```{r loading, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
library(netcopula)
library(mcmcplots)
library(coda)

load(file = file.path(path, "examples_5.RData"))
if (!.hasSlot(res, "S_q")) {
  res@S_q <- array()
  res@Sigma_q_prop <- array()
  res@rho_mu <- array()
  res@cov_mu <- array()
  res@ar_mu_vec <- array()
  res@mu_rate <- array()
  res@mu_prop <- array()
  res@tp_mu <- array()
  res@delta_prop <- array()
  res@data <- nc_data
}
```

# $\boldsymbol{\Gamma}$ fixed -- $\boldsymbol{\mu}$ and $\boldsymbol{\delta}$ unconstrained

In this section we fix the $\boldsymbol{\Gamma}$ parameters to their sample estimates, that is

```{r Gamma_fix, echo=FALSE}
cor(na.omit(nc_data@study_data[, colnames(nc_data@study_data)[regexpr("y", colnames(nc_data@study_data)) == 1]]))
```

and leave the $\boldsymbol{\mu}$ and $\boldsymbol{\delta}$ parameters unconstrained (i.e. at each iteration we do not impose the restriction that $\mu_{ikm}$ is fixed for all the arms of the same study and that $\delta_{ikm}$ is 0 for all arms different from the baseline).

```{r loading_1, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
res_mcmc <- as.mcmc(res, data = nc_data, nthin = 50, latent_var = TRUE)
res_mcmc <- add_corr(res_mcmc)
out <- summary(res, digits_summary = 5, latent_var = TRUE, print = FALSE, data = nc_data, nthin = 50)
```

## $\boldsymbol{\Gamma}$ (outcome copula correlation matrix)

```{r Gamma_1, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
gen_res("Gamma")
```

## $\boldsymbol{\Sigma}_M$ (common between-study covariance structure)

```{r Sigma_M_1, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
gen_res("Sigma_M")
```

```{r Corr_M_1, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
gen_res("Corr_M")
```

## $\boldsymbol{\mu}$ (study-specific baseline effects)

```{r mu_1, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
gen_res("mu")
```

## $\boldsymbol{\delta}$ (study-specific [random] treatment effects)

```{r delta_1, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
gen_res("delta")
```

## $\boldsymbol{d}$ (pooled treatment effects across trials)

```{r d_1, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
gen_res("d")
```

## $\boldsymbol{x}$ (latent variables)

```{r x_1, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
gen_res("x")
```


# $\boldsymbol{\Gamma}$ fixed -- $\boldsymbol{\mu}$ and $\boldsymbol{\delta}$ constrained

```{r loading_2, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
load(file = file.path(path, "examples_6.RData"))
if (!.hasSlot(res, "S_q")) {
  res@S_q <- array()
  res@Sigma_q_prop <- array()
  res@rho_mu <- array()
  res@cov_mu <- array()
  res@ar_mu_vec <- array()
  res@mu_rate <- array()
  res@mu_prop <- array()
  res@tp_mu <- array()
  res@delta_prop <- array()
  res@data <- nc_data
}
res_mcmc <- as.mcmc(res, data = nc_data, nthin = 50, latent_var = TRUE)
res_mcmc <- add_corr(res_mcmc)
out <- summary(res, digits_summary = 5, latent_var = TRUE, print = FALSE, data = nc_data, nthin = 50)
```

## $\boldsymbol{\Gamma}$ (outcome copula correlation matrix)

```{r Gamma_2, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
gen_res("Gamma")
```

## $\boldsymbol{\Sigma}_M$ (common between-study covariance structure)

```{r Sigma_M_2, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
gen_res("Sigma_M")
```

```{r Corr_M_2, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
gen_res("Corr_M")
```

## $\boldsymbol{\mu}$ (study-specific baseline effects)

```{r mu_2, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
gen_res("mu")
```

## $\boldsymbol{\delta}$ (study-specific [random] treatment effects)

```{r delta_2, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
gen_res("delta")
```

## $\boldsymbol{d}$ (pooled treatment effects across trials)

```{r d_2, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
gen_res("d")
```

## $\boldsymbol{x}$ (latent variables)

```{r x_2, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
gen_res("x")
```


# $\boldsymbol{\Gamma}$ estimated -- $\boldsymbol{\mu}$ and $\boldsymbol{\delta}$ unconstrained

```{r loading_3, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
load(file = file.path(path, "examples_7.RData"))
if (!.hasSlot(res, "S_q")) {
  res@S_q <- array()
  res@Sigma_q_prop <- array()
  res@rho_mu <- array()
  res@cov_mu <- array()
  res@ar_mu_vec <- array()
  res@mu_rate <- array()
  res@mu_prop <- array()
  res@tp_mu <- array()
  res@delta_prop <- array()
  res@data <- nc_data
}
res_mcmc <- as.mcmc(res, data = nc_data, nthin = 50, latent_var = TRUE)
res_mcmc <- add_corr(res_mcmc)
out <- summary(res, digits_summary = 5, latent_var = TRUE, print = FALSE, data = nc_data, nthin = 50)
```

## $\boldsymbol{\Gamma}$ (outcome copula correlation matrix)

```{r Gamma_3, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
gen_res("Gamma")
```

## $\boldsymbol{\Sigma}_M$ (common between-study covariance structure)

```{r Sigma_M_3, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
gen_res("Sigma_M")
```

```{r Corr_M_3, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
gen_res("Corr_M")
```

## $\boldsymbol{\mu}$ (study-specific baseline effects)

```{r mu_3, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
gen_res("mu")
```

## $\boldsymbol{\delta}$ (study-specific [random] treatment effects)

```{r delta_3, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
gen_res("delta")
```

## $\boldsymbol{d}$ (pooled treatment effects across trials)

```{r d_3, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
gen_res("d")
```

## $\boldsymbol{x}$ (latent variables)

```{r x_3, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
gen_res("x")
```
